### 2023-11-26 documents/floats/hix-intro.tex
reworked extensions section

\begin{table}
\centering
\caption[Some \hixka verbs]{Some \hixka verbs \parencites[150, 510, 513, 520]{howard2001wrought}[198]{hixkaryanaderby1985}}
\label{tab:hixintro}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
{} &     \qu{to fall} &  \qu{to be afraid} &          \qu{to walk} & \qu{to cut self} &    \qu{to be} \\
\mymidrule
\gl{1}   &  \obj{k-ehurka-} &  \obj{k-oserʲehɨ-} &  \obj{k-atarʲeknohɨ-} &   \obj{k-atama-} &  \obj{w-eʃe-} \\
\gl{2}   &  \obj{m-ehurka-} &  \obj{m-oserʲehɨ-} &  \obj{m-atarʲeknohɨ-} &   \obj{m-atama-} &  \obj{m-eʃe-} \\
\gl{1+2} &  \obj{t-ehurka-} &  \obj{t-oserʲehɨ-} &  \obj{t-atarʲeknohɨ-} &   \obj{t-atama-} &  \obj{t-eʃe-} \\
\gl{3}   &  \obj{ɲ-ehurka-} &  \obj{n-oserʲehɨ-} &  \obj{n-atarʲeknohɨ-} &   \obj{n-atama-} &  \obj{n-eʃe-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Some \hixka verbs]{Some \hixka verbs \parencites[150, 510-511, 513, 520]{howard2001wrought}[198]{hixkaryanaderby1985}}
\label{tab:hix-intro}
\begin{tabular}[t]{@{}llllll@{}}
\toprule
 & ‘to fall’ & ‘to be afraid’ & ‘to walk’ & ‘to cut self’ & ‘to be’ \\
\midrule
\gl{1} & \obj{k-ehurka-} & \obj{k-oserʲehɨ-} & \obj{k-atarʲeknohɨ-} & \obj{k-atama-} & \obj{w-eʃe-} \\
\gl{2} & \obj{m-ehurka-} & \obj{m-oserʲehɨ-} & \obj{m-atarʲeknohɨ-} & \obj{m-atama-} & \obj{m-eʃe-} \\
\gl{1+2} & \obj{t-ehurka-} & \obj{t-oserʲehɨ-} & \obj{t-atarʲeknohɨ-} & \obj{t-atama-} & \obj{t-eʃe-} \\
\gl{3} & \obj{ɲ-ehurka-} & \obj{n-oserʲehɨ-} & \obj{n-atarʲeknohɨ-} & \obj{n-atama-} & \obj{n-eʃe-} \\
\bottomrule
\end{tabular}
\end{table}

### 2023-11-26 documents/floats/ptir-verbs.tex
reworked extensions section

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112-114]{meira1998proto}{meiraDBakuriyo}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\mymidrule
\qu{go}   &  \rc{w-ɨtəmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ∅}-eʔi-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112-115]{meira1998proto}{meiraDBakuriyo}}
\label{tab:ptir-verbs}
\begin{tabular}[t]{@{}llll@{}}
\toprule
 & \PTir & \trio & \akuriyo \\
\midrule
\qu{go} & \rc{w-ɨtəmɨ-} & \obj{wɨ-tən-} & \obj{ə-təmɨ-} \\
\qu{say} & \rc{wɨ-ka-} & \obj{wɨ-ka-} & \obj{wɨ-ka-} \\
\qu{come} & \rc{w-əʔepɨ-} & \obj{w-əepɨ-} & \obj{{\normalfont ∅}-eepɨ-} \\
\qu{be-1} & \rc{w-a-} & \obj{w-a-} & \obj{{\normalfont ∅}-a-} \\
\qu{be-2} & \rc{w-eʔi-} & \obj{w-ei-} & \obj{{\normalfont ∅}-eʔi-} \\
\bottomrule
\end{tabular}
\end{table}

### 2023-11-26 documents/floats/ptirreg.tex
more tables
new approach to testing predictions from bybee's model
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
class membership of proto-taranoan 'to go down' is not reconstructible
more trimming, fixed verb citations
fixed csv output
fix abbrevs & lg names
reworked extensions section

\begin{table}
\centering
\caption[Regular \PTir \gl{s_a_} verbs]{Regular \PTir \gl{s_a_} verbs \parencites[292, 294]{triomeira1999}[87]{gildea1994akuriyo}}
\label{tab:ptirreg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{3}{l}{\qu{to bathe (\gl{intr})}} & \multicolumn{3}{l}{\qu{to sleep}} \\
{} &                     \PTir &          \trio &        \akuriyo &             \PTir &              \trio &           \akuriyo \\
\midrule
\gl{1}   &             \rc{t͡ʃ-epɨ-} &   \obj{s-epɨ-} &  \obj{t͡ʃ-epɨ-} &    \rc{t-əənɨkɨ-} &    \obj{t-əənɨkɨ-} &    \obj{k-əənɨkɨ-} \\
\gl{2}   &               \rc{m-epɨ-} &   \obj{m-epɨ-} &    \obj{m-epɨ-} &    \rc{m-əənɨkɨ-} &    \obj{m-əənɨkɨ-} &    \obj{m-əənɨkɨ-} \\
\gl{1+2} &              \rc{ke-epɨ-} &  \obj{ke-epɨ-} &   \obj{ke-epɨ-} &  \rc{kɨt-əənɨkɨ-} &  \obj{kɨt-əənɨkɨ-} &  \obj{kəʔ-əənɨkɨ-} \\
\gl{3}   &               \rc{n-epɨ-} &   \obj{n-epɨ-} &    \obj{n-epɨ-} &    \rc{n-əənɨkɨ-} &    \obj{n-əənɨkɨ-} &    \obj{n-əənɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PTir \gl{sa} verbs]{Regular \PTir \gl{sa} verbs \parencites[292, 294]{triomeira1999}[87]{gildea1994akuriyo}}
\label{tab:ptirreg}
\begin{tabular}[t]{@{}lllllll@{}}
\toprule
 & \multicolumn{3}{l}{‘to bathe (\gl{intr})’} & \multicolumn{3}{l}{‘to sleep’} \\
 & \PTir & \trio & \akuriyo & \PTir & \trio & \akuriyo \\
\midrule
\gl{1} & \rc{t͡ʃ-epɨ-} & \obj{s-epɨ-} & \obj{t͡ʃ-epɨ-} / \obj{t͡ʃ-ehpa-} & \rc{t-əənɨkɨ-} & \obj{t-əənɨkɨ-} & \obj{k-əənɨkɨ-} \\
\gl{2} & \rc{m-epɨ-} & \obj{m-epɨ-} & \obj{m-epɨ-} & \rc{m-əənɨkɨ-} & \obj{m-əənɨkɨ-} & \obj{m-əənɨkɨ-} \\
\gl{1+2} & \rc{ke-epɨ-} & \obj{ke-epɨ-} & \obj{ke-epɨ-} & \rc{kɨt-əənɨkɨ-} & \obj{kɨt-əənɨkɨ-} & \obj{kəʔ-əənɨkɨ-} \\
\gl{3} & \rc{n-epɨ-} & \obj{n-epɨ-} & \obj{n-epɨ-} & \rc{n-əənɨkɨ-} & \obj{n-əənɨkɨ-} & \obj{n-əənɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

### 2023-11-26 documents/floats/pwai-reg.tex
reworked extensions section

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{sa}) and \qu{to sleep} (\gl{sp}) in \PWai \parencites[150]{howard2001wrought}[189, 196]{hixkaryanaderby1985}[30]{waiwaihawkins1998}[209, 211]{hawkins1953waiwai}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} &    \qu{to fall} &                  &                    &     \qu{to sleep} &                 &                    \\
{} &           \PWai &           \hixka &            \waiwai &             \PWai &          \hixka &            \waiwai \\
\mymidrule
\gl{1}   &  \rc{k-eɸurka-} &  \obj{k-ehurka-} &    \obj{k-eɸɨrka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{kɨ-nɨkɨ-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &  \obj{m-ehurka-} &    \obj{m-eɸɨrka-} &    \rc{o-wɨnɨkɨ-} &  \obj{o-wnɨkɨ-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \obj{t-ehurka-} &  \obj{t͡ʃ-eɸɨrka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{tɨ-nɨkɨ-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &  \obj{ɲ-ehurka-} &    \obj{ɲ-eɸɨrka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{nɨ-nɨkɨ-} &   \obj{nɨ-wɨnɨkɨ-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{sa}) and \qu{to sleep} (\gl{sp}) in \PWai \parencites[150]{howard2001wrought}[189-190, 196]{hixkaryanaderby1985}[30]{waiwaihawkins1998}[209, 211]{hawkins1953waiwai}}
\label{tab:pwai-reg}
\begin{tabular}[t]{@{}lllllll@{}}
\toprule
 & \multicolumn{3}{l}{‘to fall’} & \multicolumn{3}{l}{‘to sleep’} \\
 & \PWai & \hixka & \waiwai & \PWai & \hixka & \waiwai \\
\midrule
\gl{1} & \rc{k-eɸurka-} & \obj{k-ehurka-} & \obj{k-eɸɨrka-} & \rc{kɨ-wɨnɨkɨ-} & \obj{kɨ-nɨkɨ-} & \obj{kɨ-wɨnɨkɨ-} \\
\gl{2} & \rc{m-eɸurka-} & \obj{m-ehurka-} & \obj{m-eɸɨrka-} & \rc{o-wɨnɨkɨ-} & \obj{o-wnɨkɨ-} & \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} & \rc{t-eɸurka-} & \obj{t-ehurka-} & \obj{t͡ʃ-eɸɨrka-} & \rc{tɨt-wɨnɨkɨ-} & \obj{tɨ-nɨkɨ-} & \obj{tɨt-wɨnɨkɨ-} \\
\gl{3} & \rc{ɲ-eɸurka-} & \obj{ɲ-ehurka-} & \obj{ɲ-eɸɨrka-} & \rc{nɨ-wɨnɨkɨ-} & \obj{nɨ-nɨkɨ-} & \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}
